DisCon Pilot Summary

### 2018-10-29 analysis/01_pilot_summary.Rmd
updated data files

write.csv(data_recency, file="../data/01_piot_summary_recency.data.csv")
data_recency <- read_csv(file="../data/01_piot_summary_recency.data.csv")
```

>>>>

write.csv(data_recency, file="../data/01_pilot_summary_recency.data.csv")
data_recency <- read_csv(file="../data/01_pilot_summary_recency.data.csv")
```
